Student Log-Data from a Randomized Evaluation of Educational Technology: A Causal Case Study

### 2020-05-05 paper.tex
change heading on balance tables
Added intro summaries to Obs Study and Mediation sections
partially addressed #5 and #8
also added subsection titles
put back (most) of the citations removed in 6ab06c2b5877d2ca531533d85ad188ed37961ae3 (in different places)
updated paper.tex

\section{Introduction}
From 2007 through 2010, the RAND corporation
conducted one of the first effectiveness trials awarded through
competitive grant programs sponsored by the US Department of
Education's Institute of Education Sciences.  The randomized
controlled trial (RCT) was
designed to estimate the effect of school-wide adoption of the
Cognitive Tutor Algebra I (CTA1) curriculum, whose centerpiece is a
computerized ``tutor'' that uses cognitive science principles to teach
Algebra I \citep{anderson1985intelligent}.
The study \citep{pane2014effectiveness} found no effects in its first year, but in
the second year of implementation students in high schools randomized to
the CTA1 condition outperformed the control group on the posttest by a fifth of a
standard deviation.

Over the course of the CTA1 study, the software administrators
gathered computer log data for students in the treatment group.
They assembled a dataset that recorded which problems each student
worked, along with timestamps, the numbers of hints requested, and the
number of errors committed for each problem.
This log data is fine-grained and rich;
education researchers could use it, and datasets like it,
to gain insight into how, why, and when educational technology works.

Along the same lines, log data presents a challenge, since it differs in
structure and size from the type of data commonly encountered in
studies of causal mechanisms.
While statistical models of log data are nearly as old as the data itself
\citep[e.g.][]{corbett1994knowledge}, data from an RCT differs in
two principal ways from more traditional domains.
RCTs feature randomization of treatment assignment, and a posttest
(or some other outcome) administered to both users and non-users.
These factors allow for causal modeling.

As educational technology booms, so do RCTs in the mold of the RAND
CTA1 study. A recent systematic review \citep{escueta2017education} cites 29
published reports of RCTs of ``computer assisted learning'' programs,
all but one of which was published since 2001. We are aware of
numerous other such RCTs planned or ongoing.
These RCTs produce log data automatically, as a bi-product.
The current case-study is
about the use of hints in CTA1, but the huge variation in products
under study, each with its own unique design, opens a wide set of opportunities to understand how features of those
products drive their effects. As one example, RAND is recently
completed an efficacy study of a different algebra tutoring system,
ALEKS. When students begin working on a particular topic in ALEKS, the
system first presents instructional material, followed by problem
solving activities, and then, if students are unsuccessful at solving
the problems, more instructional material. Some students diligently
read the initial instructional material while others skip it and dive
directly into problem solving. Is skipping the material a productive
strategy for students in terms of learning algebra, or should ALEKS be
redesigned to prevent such skipping? %Researchers should not stop at
%estimating overall average treatment effects, but
Our hope is that this paper can serve as a starting point
for researchers interested in mining the rich resource of log data.

This paper will illustrate three approaches to this type of research
using log data from the CTA1 study---specifically, data on students' use
of hints within the software.
The first approach discards the control group, and analyzes
hint-requesting in the treatment group as an observational study,
using a matching design
\citep[c.f.][]{rosenbaum2002observational}. The
second approach applies the framework of causal mediation analysis
\citep{vanderweele2015explanation,hong2015causality,imai2011unpacking} to estimate the role of
hint-requesting in the overall CTA1 treatment effect. However, since
students in the control group were unable to request hints, not all
mediational estimands are identified, and estimation methods must be
modified.
Finally, we conduct a principal stratification analysis
\citep{frangakis} to learn if students requesting different amounts of
hints experienced different treatment effects.

Our intention is to develop, demonstrate, and contrast these three
approaches to modeling log data.
A rich, and often polemic, literature surrounds principal
stratification and mediation analysis
\citep[e.g.][]{rubin2004direct,vanderweele2011principal,pearl2011principal,mealli2012refreshing,vanderweele2012comments}.
\citet{vanderweele2008simple}, \citet{jo2008causal} and others have
derived formal equivalences between parameters under certain
conditions.
Our contribution will build on this literature in two ways: first, by
providing a detailed demonstration and comparison of matching, mediation analysis,
and principal stratification on the same dataset, and second by
focusing on the applicability of these three methods in the specific
context of studying implementation data from an randomized
experiment studying educational technology (EdTech).

After a brief overview of the three causal approaches,
the next section will provide background for the case-study,
describing the CTA1 curriculum, the RAND study, and our focus on
hints.
The following three sections will present the observational study,
causal mediation, and principal stratification approaches to the hint
data.
Section \ref{sec:synthesis} will compare the three methods directly,
and discuss how they may be applied to data from other educational
technology RCTs.
Section \ref{sec:conclusion} will conclude.

The \texttt{R} and Stan code used to for all of the analyses in the paper can be found in a github repository, \url{github.com/[redacted]}.

\subsection{Brief Overview of Three Causal Approaches}
\begin{figure}
\centering
\begin{tikzpicture}[scale=1,transform shape]
	%\draw[help lines] (0,0) grid (15,3);
	\node[draw,shape=circle, inner sep=0pt,minimum size=1cm] (z) at (1,0) {$H$};
	\node[draw,shape=circle, inner sep=0pt,minimum size=1cm] (y) at +(0:3){$Y$};
	%\node[draw,shape=circle, inner sep=0pt,minimum size=1cm] (x) at (2.5,3.5){$X$};
	%\draw[->,line width=2pt](x)--(z);
	%\draw[->,line width=2pt](x)--(y);
	\draw[->,line width=2pt](z)--(y);
	\node at (2.5,-1) {(a)};

	\node[draw,shape=circle, inner sep=0pt,minimum size=1cm] (z) at (5,0) {$Z$};
	\node[draw,shape=circle, inner sep=0pt,minimum size=1cm] (y) at +(8,0){$Y$};
	\node[draw,shape=circle, inner sep=0pt,minimum size=1cm] (m) at (6.5,2){$H$};
	\draw[->,line width=2pt](z)--(m);
	\draw[->,line width=2pt](m)--(y);
	\draw[->,line width=2pt](z)--(y);
	\node at (5.4,1.2) {(1)};
	\node at (7.6,1.2) {(2)};
	\node at (6.5,.3) {(3)};
	\node at (6.5,-1) {(b)};

        \node[draw,shape=circle, inner sep=0pt,minimum size=1cm] (z) at (10,0) {$Z$};
	\node[draw,shape=circle, inner sep=0pt,minimum size=1cm] (y) at +(12,0){$Y$};
        \node (mid) at (11,0) {};
        \node[draw,shape=circle, inner sep=0pt,minimum size=1cm] (h)
        at (11,2) {$H(1)$};
	%\node[draw,shape=circle, inner sep=0pt,minimum size=1cm] (x) at (2.5,3.5){$X$};
	%\draw[->,line width=2pt](x)--(z);
	%\draw[->,line width=2pt](x)--(y);
	\draw[->,line width=2pt](z)--(y);
        \draw[->,line width=2pt](h)--(mid);
	\node at (11,-1) {(c)};

\end{tikzpicture}
\caption{A schematic representation of three causal models for
  log data: (a) an observational study estimating the effects of hints
  $H$ on posttest scores $Y$, (b) a mediation analysis estimating
  natural direct effects of treatment assignment $Z$ on $Y$ and
  indirect effects mediated by $H$, and (c) principal stratification.}
\label{mediationFig}
\end{figure}

Figure \ref{mediationFig} is a schematic representation of the three
approaches to causal modeling of log data that we will discuss in this
paper.
First, an observational study to estimate the effect of hint usage $H$
on posttest scores $Y$, is represented by panel (a).
This approach, which we will discuss in Section
\ref{sec:observational}, discards the control group from the RCT and
uses techniques from observational studies to determine if and how requesting
a greater number of hints affects posttest scores.
For the sake of illustration, we will use techniques similar to those
discussed in \citet{rosenbaum2002observational},
 \citet{hansen2009b}, and \citet{ho:etal:2007}, combining a propensity
 score matching design with methods for analyzing experiments and
 parametric modeling.
The conceptual and methodological issues we will discuss extend to
other covariate control methods as well.

Next, as represented in panel (b), we will conduct a mediation
analysis, estimating natural
indirect effects of CTA1 treatment assignment $Z$, as mediated by
$H$. That is, we will estimate the component of $Z$'s effect on $Y$ that comes about
due to $Z$'s effect on $H$---path (1)---and $H$'s effect on $Y$, path
(2).
Notice that path (2) is identical to panel (a)---the effect of $H$ on
$Y$.
We will use this equivalence to estimate and interpret indirect
effects.
As part of the mediation analysis, we will also estimate path (3), the
natural direct effect of $Z$ on $Y$---that is, the component of $Z$'s
effect on $Y$ that is not due to hints $H$.

Finally, we will estimate a principal stratification model, as represented in panel
(c).
In the principal stratification analysis, we do not model $H$ as an
intervention that could, in theory, be randomized.
Instead, we posit a variable ``$H_i(1)$,''  subject $i$'s penchant for
requesting hints \emph{if} $i$ is assigned to the treatment
condition.
Unlike $H$, $H(1)$ is well defined (if
unobserved) for all participants in the RCT.
Principal stratification treats $H(1)$ as an effect moderator or
interaction variable: $H(1)$ does not affect $Y$, but the effect of
$Z$ on $Y$ may vary as a function of $H(1)$.
This analysis will largely follow the method of \citet{aoas}, which in
turn built heavily on \citet{schwartz2011bayesian} and
\citet{jin2008principal}.

All three of these approaches are designed to model intermediate
variables---those variables, like hint usage,
that were possibly affected by $Z$ but were measured prior to $Y$.
Though they were developed for more traditional data scenarios, the
novel scenario of computer log data from an educational technology RCT
presents new and interesting challenges and opportunities.

@@

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Tue Feb 11 09:12:59 2020
\begin{table}[ht]
\centering
\begin{tabular}{rllccc}
  \hline
  &&&&\multicolumn{2}{c}{Sensitivity Intervals}\\
 Weights&Estimate&Std. Error&CI&[Pretest]&[Ethnicity] \\
 \hline
OLS & -0.18 & 0.04 & [-0.25,-0.10] & [-0.41,0.06] & [-0.30,-0.05] \\ 
  ATE & -0.12 & 0.05 & [-0.23,-0.02] & [-0.45,0.20] & [-0.29,0.04] \\ 
  TOT & -0.14 & 0.06 & [-0.25,-0.03] & [-0.47,0.19] & [-0.31,0.03] \\ 
   \hline
\end{tabular}
\caption{Estimates, standard errors, and sensitivity analysis of the weighted average effect of hint usage on posttest scores, under different weighting schemes.} 
\label{tab:matchResults}
\end{table}

@@

\subsection{Stan Code}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
## data{
## //Sample sizes
##  int<lower=1> N; // total number of obs (long format)
##  int<lower=1> nstud; // # students
##  int<lower=1> nsec; // # sections (problems nested in sections)
## 
## // indices
##  int<lower=1,upper=nstud> studentM[N]; //for each obs, which student?
##  int<lower=1,upper=nsec> section[N]; // for each obs, which section?
## 
## // data data
##  int<lower=0,upper=1> hint[N]; // for each obs, was a hint requested?
## 
## }
## parameters{
## 
##  vector[nstud] eta; // ability parameter
##  real<lower=0,upper=1> p1; // mixing proportion
##  //ordered[2] mu;             // locations of mixture components
##  real<upper=0> mu0; //location of mixture component 0
##  vector<lower=0>[2] sigma;  // scales of mixture components
## 
##  real delta[nsec]; // section difficulty parameter
##  //real<lower=0> sigSec; // scale of difficulty parameters
## 
## }
## transformed parameters{
##  real<lower=0> mu1; // location of mixture component 1
##  mu1= -(1-p1)/p1*mu0;
## }
## model{
##  // logs of mixing proportions to save time
##  real log_p1=log(p1);
##  real log_p0=log(1-p1);
## 
## // linear predictor for logit model
##  real linPred[N];
## 
## // priors
##  sigma ~ lognormal(0, 2);
##  mu0 ~ normal(0, 2);
## // sigSec ~ lognormal(0,2);
##  p1~ beta(2,2); // I'd rather the groups have similar sizes
## 
## // model for section difficulty parameters
##  delta~normal(0,3);//sigSec);
## 
## // Rasch model for hint requests
##  for(i in 1:N)
##   linPred[i]= eta[studentM[i]]-delta[section[i]];
## 
##  hint~bernoulli_logit(linPred);
## 
## 
## // mixture model for ability parameters
##  for(n in 1:nstud)
##   target += log_sum_exp(log_p0+normal_lpdf(eta[n]|mu0,sigma[1]),
## 			log_p1+normal_lpdf(eta[n]|mu1,sigma[2]));
## 
## }
\end{verbatim}
\end{kframe}
\end{knitrout}
%\clearpage
\section{Covariate Balance Before and After Matching}
% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Tue Feb 11 09:12:59 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrrrr}
  &\multicolumn{3}{c}{Unmatched}&\multicolumn{3}{c}{Matched}\\
 \hline
 & std.diff & z &  & std.diff & z &  \\ 
  \hline
grade9 & -0.34 & -7.05 & *** & 0.03 & 0.44 &     \\ 
  gradehigher & 0.34 & 7.05 & *** & -0.03 & -0.44 &     \\ 
  raceWhiteAsian & -0.64 & -12.83 & *** & 0.03 & 0.75 &     \\ 
  raceBlackMulti & 0.23 & 4.71 & *** & 0.01 & 0.24 &     \\ 
  raceHispAIAN & 0.51 & 10.35 & *** & -0.05 & -0.98 &     \\ 
  xirt & -0.52 & -10.54 & *** & 0.09 & 1.82 & .   \\ 
  spectypical & -0.16 & -3.32 & *** & 0.03 & 0.48 &     \\ 
  specspeced & 0.34 & 7.07 & *** & -0.10 & -1.44 &     \\ 
  specgifted & -0.14 & -3.03 & **  & 0.06 & 1.16 &     \\ 
  esl0 & -0.37 & -7.70 & *** & 0.04 & 0.63 &     \\ 
  esl1 & 0.37 & 7.70 & *** & -0.04 & -0.63 &     \\ 
  stateCT & 0.58 & 11.81 & *** & -0.00 & 0.00 &     \\ 
  stateKY & -0.36 & -7.51 & *** & -0.00 & 0.00 &     \\ 
  stateLA & -0.08 & -1.68 & .   & -0.00 & 0.00 &     \\ 
  stateMI & -0.36 & -7.51 & *** & 0.00 & 0.00 &     \\ 
  stateTX & 0.43 & 8.77 & *** & 0.00 & 0.00 &     \\ 
   \hline
\end{tabular}
\caption{Covariate balance (standardized differences and Z-scores) before and after the propensity score match.} 
\label{tab:balance}
\end{table}

>>>>

\section{Introduction}
From 2007 through 2010, the RAND corporation
conducted one of the first effectiveness trials awarded through
competitive grant programs sponsored by the US Department of
Education's Institute of Education Sciences.  The randomized
controlled trial (RCT) was
designed to estimate the effect of school-wide adoption of the
Cognitive Tutor Algebra I (CTA1) curriculum, whose centerpiece is a
computerized ``tutor'' that uses cognitive science principles to teach
Algebra I \citep{anderson1985intelligent}.
The study \citep{pane2014effectiveness} found no effects in its first year, but in
the second year of implementation students in high schools randomized to
the CTA1 condition outperformed the control group on the posttest by a fifth of a
standard deviation.
As educational technology (EdTech) booms, so do RCTs in the mold of the RAND
CTA1 study. A recent systematic review \citep{escueta2017education} cites 29
published reports of RCTs of ``computer assisted learning'' programs,
all but one of which was published since 2001. We are aware of
numerous other such RCTs planned or ongoing.

RCTs are invaluable tools for estimating these programs'
efficacy. However, the interventions they study are highly
multifaceted and complex. Each classroom, and each student within
those classrooms, may use an EdTech application in a different way;
presumably, the application's efficacy depends on these usage
decisions.
Similarly, EdTech applications often include a number of optional
features---to what extent do each of these drive the program's
effectiveness?
The data collected during typical education RCTs---data on treatment
assignments, outcomes, a standard set of demographics, and possibly a
pretest---offer limited options for studying treatment effect
heterogeneity, and offer no information on how the intervention was
implemented.

However, with little extra effort, researchers studying EdTech can
gather rich implementation data over the course of an RCT.
For instance, the software administrators running the CTA1 RCT
gathered computer log data for students in the treatment group.
They assembled a dataset that recorded which problems each student
worked, along with timestamps, the numbers of hints requested, and the
number of errors committed for each problem.
Analogous log data is (or may be) collected from other EdTech RCTs.
As one example, RAND recently
completed an efficacy study of a different algebra tutoring system,
ALEKS, and gathered student log data in order to study
implementation.
An ongoing research project is using this dataset to
study instructional material within ALEKS: when students begin working on a particular topic in ALEKS, the
system first presents instructional material, followed by problem
solving activities, and then, if students are unsuccessful at solving
the problems, more instructional material. Some students diligently
read the initial instructional material while others skip it and dive
directly into problem solving. Is skipping the material a productive
strategy for students in terms of learning algebra, or should ALEKS be
redesigned to prevent such skipping? %Researchers should not stop at
%estimating overall average treatment effects, but
% Our hope is that this paper can serve as a starting point
% for researchers interested in mining the rich resource of log data to
% answer these types of questions.

Analysis of log data from EdTech RCTs could, in principle, lead to
insights on the relationship between implementation and effectiveness.
Using log data, researchers could investigate how the product was
actually implemented, as well as what aspects of implementation
correlate with higher (or lower) treatment effects, or which features
of the program drive its effects.

However, answering these questions requires new statistical tools.
These tools must simultaneously surmount three challenges: first,
implementation is not typically randomized, so the relationship
between log data and outcomes is likely confounded. Second,
log data is only gathered from students assigned to use the
intervention, and not from the control group. Third, log datasets have
a complex structure---often a large number of granular observations of several types
gathered over the course of each student's engagement with the
program.

This paper will illustrate three approaches to this type of research
using log data from the CTA1 study---specifically, data on students' use
of hints within the software.
We will attempt to answer two related questions: first, what role does
the availability of hints play in driving the overall CTA1 treatment
effect, and second, can requesting hints more often lead to a larger
treatment effect.
The first approach we consider discards the control group, and analyzes
hint-requesting in the treatment group as an observational study,
using a matching design
\citep[c.f.][]{rosenbaum2002observational}. The
second approach applies the framework of causal mediation analysis
\citep{vanderweele2015explanation,hong2015causality,imai2011unpacking} to estimate the role of
hint-requesting in the overall CTA1 treatment effect. However, since
students in the control group were unable to request hints, not all
mediational estimands are identified, and estimation methods must be
modified.
Finally, we conduct a principal stratification analysis
\citep{frangakis} to learn if students requesting different amounts of
hints experienced different treatment effects.

Our intention is to develop, demonstrate, and contrast these three
approaches to modeling log data.
A rich, and often polemic, literature surrounds principal
stratification and mediation analysis
\citep[e.g.][]{rubin2004direct,vanderweele2011principal,pearl2011principal,mealli2012refreshing,vanderweele2012comments}.
\citet{vanderweele2008simple}, \citet{jo2008causal} and others have
given conditions under which certain principal stratification and mediational
estimands coincide.
Our contribution will build on this literature in two ways: first, by
providing a detailed demonstration and comparison of matching, mediation analysis,
and principal stratification on the same dataset, and second by
focusing on the applicability of these three methods in the specific
context of studying implementation data from an randomized
experiment studying educational technology.

The following section will provide background for the case-study,
describing the CTA1 curriculum, the RAND study, and our focus on
hints.
The following three sections will present an observational study,
which discards the control group altogether and estimates the effect
of hint requests on posttest scores;
causal mediation, which decomposes the overall treatment effect into a
component driven by hint requests and another driven by other
mechanisms; and principal stratification, which estimates separate
treatment effects for groups of students who would request hints
differently, if assigned to treatment.
As it turns out, these analyses appear to give contradictory
results---the observational study and mediation analysis estimate a
negative effect of requesting hints, while the principal
stratification analysis finds that students who request more hints
experience larger overall treatment effects.
Section \ref{sec:synthesis} will contrast these findings (including a
possible reconciliation), compare the three methods generally,
and discuss how they may be applied to data from other educational
technology RCTs.
Section \ref{sec:conclusion} will conclude.

The \texttt{R} and Stan code used to for all of the analyses in the paper can be found in a github repository, \url{https://github.com/adamSales/logDataCaseStudy}.

@@

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Mon Apr 27 14:45:08 2020
\begin{table}[ht]
\centering
\begin{tabular}{rllccc}
  \hline
  &&&&\multicolumn{2}{c}{Sensitivity Intervals}\\
 Weights&Estimate&Std. Error&CI&[Pretest]&[Ethnicity] \\
 \hline
OLS & -0.18 & 0.04 & [-0.25,-0.10] & [-0.41,0.06] & [-0.30,-0.05] \\ 
  ATE & -0.12 & 0.05 & [-0.23,-0.02] & [-0.45,0.20] & [-0.29,0.04] \\ 
  TOT & -0.14 & 0.06 & [-0.25,-0.03] & [-0.47,0.19] & [-0.31,0.03] \\ 
   \hline
\end{tabular}
\caption{Estimates, standard errors, and sensitivity analysis of the weighted average effect of hint usage on posttest scores, under different weighting schemes.} 
\label{tab:matchResults}
\end{table}

@@

\subsection{Stan Code}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
## data{
## //Sample sizes
##  int<lower=1> N; // total number of obs (long format)
##  int<lower=1> nstud; // # students
##  int<lower=1> nsec; // # sections (problems nested in sections)
## 
## // indices
##  int<lower=1,upper=nstud> studentM[N]; //for each obs, which student?
##  int<lower=1,upper=nsec> section[N]; // for each obs, which section?
## 
## // data data
##  int<lower=0,upper=1> hint[N]; // for each obs, was a hint requested?
## 
## }
## parameters{
## 
##  vector[nstud] eta; // ability parameter
##  real<lower=0,upper=1> p1; // mixing proportion
##  //ordered[2] mu;             // locations of mixture components
##  real<upper=0> mu0; //location of mixture component 0
##  vector<lower=0>[2] sigma;  // scales of mixture components
## 
##  real delta[nsec]; // section difficulty parameter
##  //real<lower=0> sigSec; // scale of difficulty parameters
## 
## }
## transformed parameters{
##  real<lower=0> mu1; // location of mixture component 1
##  mu1= -(1-p1)/p1*mu0;
## }
## model{
##  // logs of mixing proportions to save time
##  real log_p1=log(p1);
##  real log_p0=log(1-p1);
## 
## // linear predictor for logit model
##  real linPred[N];
## 
## // priors
##  sigma ~ lognormal(0, 2);
##  mu0 ~ normal(0, 2);
## // sigSec ~ lognormal(0,2);
##  p1~ beta(2,2); // I'd rather the groups have similar sizes
## 
## // model for section difficulty parameters
##  delta~normal(0,3);//sigSec);
## 
## // Rasch model for hint requests
##  for(i in 1:N)
##   linPred[i]= eta[studentM[i]]-delta[section[i]];
## 
##  hint~bernoulli_logit(linPred);
## 
## 
## // mixture model for ability parameters
##  for(n in 1:nstud)
##   target += log_sum_exp(log_p0+normal_lpdf(eta[n]|mu0,sigma[1]),
## 			log_p1+normal_lpdf(eta[n]|mu1,sigma[2]));
## 
## }
\end{verbatim}
\end{kframe}
\end{knitrout}
%\clearpage
\section{Covariate Balance Before and After Matching}
% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Mon Apr 27 14:45:09 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrrrr}
  &\multicolumn{3}{c}{Unmatched}&\multicolumn{3}{c}{Matched}\\
 \hline
 & std.diff & z &  & std.diff & z &  \\ 
  \hline
grade9 & -0.34 & -7.05 & *** & 0.03 & 0.44 &     \\ 
  gradehigher & 0.34 & 7.05 & *** & -0.03 & -0.44 &     \\ 
  raceWhiteAsian & -0.64 & -12.83 & *** & 0.03 & 0.75 &     \\ 
  raceBlackMulti & 0.23 & 4.71 & *** & 0.01 & 0.24 &     \\ 
  raceHispAIAN & 0.51 & 10.35 & *** & -0.05 & -0.98 &     \\ 
  xirt & -0.52 & -10.54 & *** & 0.09 & 1.82 & .   \\ 
  spectypical & -0.16 & -3.32 & *** & 0.03 & 0.48 &     \\ 
  specspeced & 0.34 & 7.07 & *** & -0.10 & -1.44 &     \\ 
  specgifted & -0.14 & -3.03 & **  & 0.06 & 1.16 &     \\ 
  esl0 & -0.37 & -7.70 & *** & 0.04 & 0.63 &     \\ 
  esl1 & 0.37 & 7.70 & *** & -0.04 & -0.63 &     \\ 
  stateCT & 0.58 & 11.81 & *** & -0.00 & 0.00 &     \\ 
  stateKY & -0.36 & -7.51 & *** & -0.00 & 0.00 &     \\ 
  stateLA & -0.08 & -1.68 & .   & -0.00 & 0.00 &     \\ 
  stateMI & -0.36 & -7.51 & *** & 0.00 & 0.00 &     \\ 
  stateTX & 0.43 & 8.77 & *** & 0.00 & 0.00 &     \\ 
   \hline
\end{tabular}
\caption{Covariate balance (standardized differences and Z-scores) before and after the propensity score match.} 
\label{tab:balance}
\end{table}
